---
title: "p8105_hw5_xz2809"
author: "Coco"
date: "11/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

##load files 
Start with a dataframe containing all file names; the list.files function will help
```{r}
files_df = list.files(path = "./data") %>% 
  as.data.frame()

colnames(files_df) = "subject_id"
```

##clean data
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

```{r}
read_files = function(x){
    read_csv(paste0("./data/",x))
}

df = map(files_df[ ,1],read_files)

mydf = df[[1]]
for (i in 2:20) {
  mydf = rbind(mydf,df[[i]])
}
mydf <- cbind(files_df, mydf) 
```
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
mydf = mydf %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  mutate(week = str_replace(week,"week_",""),
         subject_id = str_replace(subject_id,".csv",""),
         overall_id = factor(subject_id)) %>% 
  separate(subject_id, into = c("arms", "id"),sep = "_")
```
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
mydf %>% 
  ggplot(aes(x = as.numeric(week), y=as.numeric(value),color = overall_id))+
  geom_line()
```




